ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
Reorganise figures
fit table
1st_topic

    \topic{odgi build, view \& validate} pangenome graphs are commonly
    represented by a subset of Graphical Fragment Assembly (GFAv1)
    format \citep{GFAv1}; \cmd{odgi build} and \cmd{odgi view} allow
    to convert graphs from GFA to \odgi\ format and vice versa. In the
    variation graph model, paths have to respect the graph's topology:
    this can be verified with \cmd{odgi validate}, to ensure no
    errors in the input or edited graphs.

@@

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
        \processtable{Centromeres extraction comparison using \odgi\ and VG
        \label{tab:02}} {
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}

>>>>

    \topic{odgi build, view \& validate} pangenome graphs are
    represented by a subset of the textual Graphical Fragment Assembly
    (GFAv1) format\citep{GFAv1}; \cmd{odgi build} and \cmd{odgi view}
    convert graphs from GFA to the \odgi\ format and vice versa.
    \cmd{odgi validate} ascertains the graph data is correct, such as
    validating that paths respect the graph's topology.

@@

    %TODO to repeat on a bigger machine to avoid vg crashing
    \begin{table}[!t]
        \processtable{Centromeres extraction comparison using \odgi\ and VG
          \label{tab:02}} {
          \resizebox{.99\columnwidth}{!}{
            \begin{tabular}{@{}lllll@{}}
                \toprule Operation & Tool & Runtime (mm:ss) & Memory (GB) & Output size (GB)    \\
                \midrule
                Format conversion                           &       &       &                   \\
                                    & \cmd{odgi build}      & 1:35  & 10.39 & 5.4               \\
                                    & \cmd{vg convert}      & 8:14  & 28.43 & 6.1               \\
                Subgraph extraction                         &       &       &                   \\
                                    & \cmd{odgi extract}    & 1:15  & 9.43  & 2.7               \\
                                    & \cmd{vg chunk}        & 21:09 & 59.33 & 1.7               \\
                \botrule
            \end{tabular}}}
